Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-12-11 text/sparks.tex
Fix 10*10^ should just be 10^

\caption[Example population dynamic black swans from the Global Population
  Dynamics Database and a description of their causes.]{Example population dynamic black swans from the Global Population
  Dynamics Database and a description of their causes. Red and blue dots
  indicate downward and upward events that have a $10 \cdot 10^{-4}$ probability or less of
  occurring if the population dynamics were explained by a Gompertz model
  with normally distributed process noise. These populations are
  a sample from the heavy-tailed populations we could verify
  (Table~\ref{tab:causes-supp}).}\\

>>>>

\caption[Example population dynamic black swans from the Global Population
  Dynamics Database and a description of their causes.]{Example population dynamic black swans from the Global Population
  Dynamics Database and a description of their causes. Red and blue dots
  indicate downward and upward events that have a $10^{-4}$ probability or less of
  occurring if the population dynamics were explained by a Gompertz model
  with normally distributed process noise. These populations are
  a sample from the heavy-tailed populations we could verify
  (Table~\ref{tab:causes-supp}).}\\
